---
title: "Replication of Payne et al. (2013, experiment 2)"
subtitle: "Analyses"
author: "Ian Hussey & Jamie Cummins"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r include=FALSE}

# set options for knitr output
knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE)

# turn off scientific notation so that p values print nicely
options(scipen=999)

```

```{r setup, message=FALSE, warning=FALSE}

# dependencies
library(tidyverse)
library(knitr)
library(kableExtra)
library(Partiallyoverlapping)
library(janitor)

# function to round all numeric vars in a data frame
round_df <- function(df, n_digits = 3) {
  df %>% mutate_if(is.numeric, janitor::round_half_up, digits = n_digits)
}

# get data 
data_processed <- read_csv("../data/processed/data_processed_participant_level.csv")

# exclusions
data_processed_exclusions <- data_processed %>%
  filter(complete_data == TRUE)

```

# Demographics

Analytic sample after exclusions.

```{r age and gender}

# Gender
data_processed_exclusions %>%
  mutate(gender = tolower(gender)) %>%
  dplyr::count(gender) %>%
  kable() %>%  # print nicer looking table
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

# Age mean and SD
data_processed_exclusions %>%
  mutate(age = as.numeric(as.character(age))) %>%
  summarise("age (mean)" = mean(age), "age (standard deviation)" = sd(age)) %>%
  round_df(2) %>%
  kable() %>%  # print nicer looking table
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

# Hypothesis tests

## Hypothesis 1: Magnitude of Standard AMP effect compared to the skip-AMP effect

Payne et al. hypothesized that, if participants are influence-aware in the AMP, then AMP effects in the standard AMP should be larger than those of the skip AMP.

Some participants may skip all trials of the skip AMP, and thus have no score. While they could simply be excluded in order to run a paired samples t-test, these values are Missing Not At Random - indeed, they are missing because of their extremely high influence rate. As such, their exclusion would distort results. 

In order to overcome this, we employed a "partially overlapping t test". Specifically, Derrick, Toher & White (2017) developed a method to assess partially overlapping samples. That is, neither a dependent nor independent t test, but a mixed t test containing some independent and some dependent data. Participants who demonstrated an influence rate of close to 100% have missing skip AMP effects. Their corresponding AMP effects are entered as independent data. Participants that have both AMP and skip AMP data are entered as dependent.

```{r}

# subset data
data_subset <- data_processed_exclusions %>%
  select(AMP_effect_positive_negative, skip_AMP_effect_positive_negative) 

Partover.test(x1 = pull(filter(data_subset, is.na(skip_AMP_effect_positive_negative)),
                        AMP_effect_positive_negative),
              x2 = pull(filter(data_subset, is.na(AMP_effect_positive_negative)),
                        skip_AMP_effect_positive_negative),
              x3 = pull(na.omit(data_subset), 
                        AMP_effect_positive_negative), 
              x4 = pull(na.omit(data_subset), 
                        skip_AMP_effect_positive_negative),
              var.equal = FALSE) %>%
  unlist(.) %>%
  data.frame(value = .) %>%
  rownames_to_column(var = "key") %>%
  spread(key, value) %>%
  mutate(t = round(statistic, 2),
         df = round(parameter, 2),
         difference_in_means = round(estimate, 2),
         p.value = as.character(p.value)) %>%
  select(t, df, p = p.value, difference_in_means) %>%
  kable() %>%  # print nicer looking table
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```
